Ottenere Docker per Ubuntu.(https://docs.docker.com/engine/installation/linux/ubuntu/)

This installation procedure for users who are unfamiliar with package managers, and just want to try out the Getting Started tutorial while running Docker on Linux. If you are comfortable with package managers, prefer not to use curl, or have problems installing and want to troubleshoot, please use our apt and yum repositories instead for your installation.

    Log into your Ubuntu installation as a user with sudo privileges.

    Verify that you have curl installed.
\begin{verbatim}
     $ which curl

    If curl isn’t installed, install it after updating your manager:

     $ sudo apt-get update
     $ sudo apt-get install curl

    Get the latest Docker package.

     $ curl -fsSL https://get.docker.com/ | sh

    The system prompts you for your sudo password. Then, it downloads and installs Docker and its dependencies.

    Note: If your company is behind a filtering proxy, you may find that the apt-key command fails for the Docker repo
    during installation. To work around this, add the key directly using the following:

     $ curl -fsSL https://get.docker.com/gpg | sudo apt-key add -
\end{verbatim}
*IN ADDITION*
If you would like to use Docker as a non-root user, you should now consider
adding your user to the "docker" group with something like:

  sudo usermod -aG docker linuxmintx64-2

Remember that you will have to log out and back in for this to take effect!

# NON FUNZIONA
Recommended extra packages
You need curl if you don’t have it. Unless you have a strong reason not to, install the linux-image-extra-* packages, which allow Docker to use the aufs storage drivers. This applies to all versions of Ubuntu.

$ sudo apt-get update

$ sudo apt-get install curl \
    linux-image-extra-$(uname -r) \
    linux-image-extra-virtual
#

DOPO L'INSTALLAZIONE
*procedo ccon la verifica dell'installazione. ()
*procedere con esercizoio di base. ()
